Comparative Analysis of Approximation Algorithms for Solving TSP

### 2018-04-25 tex/paper.tex
ResultsSectionReviewed

	\section{Dataset}
	Datasets for TSP problem contain a wide variety of formats. Cities across a country, VLSI nodes or traveling across the Mona Lisa drawing. But they are all similar in the aspect of the data structure. The structure is a 2-D coordinate point system with euclidean distances as the distance between nodes.
	For our work we selected the Uruguay dataset from the national dataset collection\cite{UY734} to be used to assess the four algorithms in this survey in terms of runtime performance and how close are their solutions compared to the dataset know optimal solution. Uruguay dataset is characterized by 
	\begin{itemize}
		\item 734 unique points (no duplicates)
		\item Optimal tour of length 79114
	\end{itemize}
	\begin{figure}[h!]
		\centering
		\includegraphics[scale=0.3]{./uypoints.jpg}
		\caption{XY coordinate representation of Uruguay dataset}
		\label{fig:uruguay}
	\end{figure}
	A graphical representation of the coordinates of the dataset is shown in figure \ref{fig:uruguay}

@@

	\section{Results}
	The codes to solve the TSP problem\cite{Kirk14}\cite{mathwork}\cite{Jang02}\cite{Jevtic14}\cite{Ibrahim15} were executed on both Matlab and Octave, taking into consideration the resulting output path length and the execution time. All the test conducted were repeated ten times each in order to see how well the algorithms can improve in both criteria. In the program using GA, the running time on Octave was 45,362 seconds (approximately 12.5 hours). Due to the long duration of the test runtime this experiment was not repeated except two times. While the running time on Matlab provided a minimum time of 76 seconds on the first trial and a maximum time of 118.9 seconds on the 8$^{th}$ trial, the shortest path found was on the 6$^{th}$ iteration, of length 226,854.7 which is 65\% within the optimal solution. While the optimized GA algorithms produced much better running times for the same number of iterations with a minimum of 23.8 seconds on th first run and a maximum of 32.1 seconds on the 7$^{th}$ run, the final path length didn't differ much from the previous implementation, a path of length 200,068 was found which is 60\% within the optimal solution. At a much faster running time and a slight improvement of 5\%, the seconds GA algorithm can be run for longer iterations and thus providing much better results. Results of GA run is shown in fig.\ref{fig:GAalgorithm}

@@

	The previous results are tabulated in Table \ref{tab:results}.

	\begin{table}[h!]
		\caption{Results of TSP algorithms}
		\scalebox{0.8}{
		\begin{tabular}{cccccc} 
			\hline
			{Algorithm} &{GA} &{SA} & {NN} & {ACO} &{OGA}\\

@@

			\hline
		\end{tabular}}
	\label{tab:results}
	\end{table}

@@

	Within the considered algorithms, SA managed to produce the most optimal solution at a $11.34\%$ of the optimal solution, however, it was one of the slowest implementations. The NN algorthim, although a simple algorithm, produced the second most optimal solution only at $18\%$ from the global optimum and interestingly with the fastest runtime between all the other algorithms. On the contrary, ACO proved to be the least correct algorithm with $91.5\%$ from the global optimum. Another important finding, is that the GA, the newer optimized implementation have managed to improve the runtime performance considerably.

>>>>

@@

	\section{Results}

	Datasets for TSP problem contain a wide variety of formats. Cities across a country, VLSI nodes or traveling across the Mona Lisa drawing are examples of these formats. But they are all similar in the data structure which is a 2-D coordinate point system with euclidean distances as the distance between nodes.
	For our work we selected the Uruguay dataset from the national dataset collection\cite{UY734} to be used to assess the four algorithms in this survey in terms of runtime performance and how close are their solutions compared to the dataset know optimal solution. Uruguay dataset is characterized by 
	\begin{itemize}
		\item 734 unique points (no duplicates)
		\item Optimal tour of length 79,114
	\end{itemize}
	A graphical representation of the coordinates of the dataset is shown in figure \ref{fig:uruguay}
	\begin{figure}[h!]
		\centering
		\includegraphics[scale=0.3]{./uypoints.jpg}
		\caption{XY coordinate representation of Uruguay dataset}
		\label{fig:uruguay}
	\end{figure}

	Another two similar datasets from the national dataset collection were used to verify the results. The two datasets are Oman and Western Sahara. These datasets vary gravely in the number of points as Oman has 1,979 points with an optimal tour of 86,891 while Western Sahara has only 29 points with an optimal tour of 27,603.

	The codes to solve the TSP problem\cite{Kirk14}\cite{mathwork}\cite{Jang02}\cite{Jevtic14}\cite{Ibrahim15} were executed on both Matlab and Octave, taking into consideration the resulting output path length and the execution time. All the test conducted were repeated ten times each in order to see how well the algorithms can improve in both criteria. The generated path efficiency is calculated as the percentage of the increase in the resulting path length over the optimal path.
	$\frac{\textit{Detected Path Length} - \textit{Optimal Path Length}}{Detected Path Length} * 100 $

	In the program using GA, the running time on Octave was 45,362 seconds (approximately 12.5 hours). Due to the long duration of the test runtime this experiment was not repeated except two times. While the running time on Matlab provided a minimum time of 76 seconds on the first trial and a maximum time of 118.9 seconds on the 8$^{th}$ trial, the shortest path found was on the 6$^{th}$ iteration, of length 226,854.7 which is 65\% within the optimal solution. Another implementation of GA, Optimized GA, that is mentioned in \cite{mathwork} was tested. This is a toolbox provided by MathWorks for optimization problems, where a search for a global maximum or minimum is required.  While the optimized GA algorithm produced much better running times for the same number of iterations with a minimum of 23.8 seconds on th first run and a maximum of 32.1 seconds on the 7$^{th}$ run, the final path length didn't differ much from the previous implementation, a path of length 200,068 was found which is 60\% within the optimal solution. At a much faster running time and a slight improvement of 5\%, the seconds GA algorithm can be run for longer iterations and thus providing much better results. Results of GA run is shown in fig.\ref{fig:GAalgorithm}

@@

	The previous results are tabulated in Table \ref{tab:resultsUruguay}.

	\begin{table}[h!]
		\caption{Results on Uruguay Dataset}
		\scalebox{0.8}{
		\begin{tabular}{cccccc} 
			\hline
			{Algorithm} &{GA} &{SA} & {NN} & {ACO} &{OGA}\\

@@

			\hline
		\end{tabular}}
	\label{tab:resultsUruguay}
	\end{table}

	\begin{table}[h!]
		\caption{Results on Western Sahara Dataset}
		\scalebox{0.8}{
			\begin{tabular}{cccccc} 
				\hline
				{Algorithm} &{GA} &{SA} & {NN} & {ACO} &{OGA}\\

				\hline
				{\multirow{2}{*}{Matlab}} & {8.5} &{0.99}& {0.0787} &{0.11} &{0.87} \\
				running time & & & & & \\

				\hline
				{\multirow{2}{*}{Generated}} & {27,603} &{27,603}& {32,161} &{35,142} &{27,603} \\
				path length & & & & & \\

				\hline
				{\multirow{2}{*}{Efficiency}} & {0\%} &{0\%}& {16.5\%} &{21.5\%} &{0\%} \\
				of path & & & & & \\

				\hline
		\end{tabular}}
		\label{tab:resultsSahara}
	\end{table}

	\begin{table}[h!]
		\caption{Results on Oman Dataset}
		\scalebox{0.8}{
			\begin{tabular}{cccccc} 
				\hline
				{Algorithm} &{GA} &{SA} & {NN} & {ACO} &{OGA}\\

				\hline
				{\multirow{2}{*}{Matlab}} & {162} &{552}& {178} &{134.5} &{45.7} \\
				running time & & & & & \\

				\hline
				{\multirow{2}{*}{Generated}} & {464,033} &{102,904}& {110,694} &{1,992,667} &{704,404} \\
				path length & & & & & \\

				\hline
				{\multirow{2}{*}{Efficiency}} & {81.27\%} &{15.56\%}& {21.5\%} &{95.6\%} &{87.6\%} \\
				of path & & & & & \\

				\hline
		\end{tabular}}
		\label{tab:resultsOman}
	\end{table}

	The results shown in table \ref{tab:resultsSahara} \ref{tab:resultsOman} verify the results conducted on Uruguay dataset. Since GA, SA, and OGA search for a global optimum solution with gradual enhancement between each iteration, the three algorithms achieved the optimal solution on the smaller Western Sahara dataset unlike NN. ACO achieved much better efficiency than larger datasets.
	Although the smaller dataset provided better path efficiency, the running time was biased as most algorithms ran very fast and almost all algorithms ran in under 1 second yet, NN still managed to run about 10x faster than the other algorithms.

@@

	Within the considered algorithms, SA managed to produce the most optimal solution at a $11.34\%$ of the optimal solution, however, it was one of the slowest implementations. The NN algorthim, although a simple algorithm, produced the second most optimal solution only at $18\%$ from the global optimum and interestingly with the fastest runtime between all the other algorithms. On the contrary, ACO proved to be the least correct algorithm with $91.5\%$ from the global optimum. Another important finding, is that for the GA, the newer optimized implementation have managed to improve the runtime performance considerably.
